Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
adding adhesion.tex back to repo

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a planar shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the planar shear flow $\uu =
\dot\gamma(y,0)$, where $\dot\gamma$ is the shear rate.  To be
consistent with simulations in previous sections, the vesicles have a
length of $2\pi$ for all reduced areas.  The initial placement of the
vesicles is chosen so that the flow dives them towards one another in a
head-on collision.  In the absence of adhesion, once the vesicles are
sufficiently close, they are deflected to opposite sides of the $y$
axis, pass one another, and then separate. This head-on collision
process of two vesicles or capsules in a planar shear flow is found to
be similar between two-~\cite{LacMorelBarthes-Biesel2007_JFM,
RahimianVeerapaneniBiros2010_JCP} and
three-dimensions~\cite{LacBarthes-Biesel2008_PoF,
OmoriIshikawaImaiYamaguchi2013_JBiomechics,
RahimianVeerapaneniZorinBiros2015_JCP}.  However, in the presence of
adhesion, the vesicles can form a doublet for certain values of the
separation distance $\delta$, Hamaker constant $\mathcal{H}$, shear rate
$\dot\gamma$, and reduced area $\Delta A$.  If a doublet does form, then
it undergoes a periodic motion with a period that depends on the same
parameters.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a planar shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the planar shear flow $\uu =
\dot\gamma(y,0)$, where $\dot\gamma$ is the shear rate.  To be
consistent with simulations in previous sections, the vesicles have a
length of $2\pi$ for all reduced areas.  The initial placement of the
vesicles is chosen so that the flow dives them towards one another in a
head-on collision.  In the absence of adhesion, once the vesicles are
sufficiently close, they are deflected to opposite sides of the $y$
axis, pass one another, and then separate. This head-on collision
process of two vesicles or capsules in a planar shear flow is found to
be similar between
two-~\cite{Breyiannis-Pozrikidis:2000,RahimianVeerapaneniBiros2010_JCP}
, RahimianVeerapaneniBiros2010_JCP} and
three-dimensions~\cite{LacMorelBarthes-Biesel2007_JFM,LacBarthes-Biesel2008_PoF,
OmoriIshikawaImaiYamaguchi2013_JBiomechics,
RahimianVeerapaneniZorinBiros2015_JCP}.  However, in the presence of
adhesion, the vesicles can form a doublet for certain values of the
separation distance $\delta$, Hamaker constant $\mathcal{H}$, shear rate
$\dot\gamma$, and reduced area $\Delta A$.  If a doublet does form, then
it undergoes a periodic motion with a period that depends on the same
parameters.
